---
title: "Favorite stadium across mexico"
author: "Irving Veliz"
date: "8/6/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Description 

Create a web page using R Markdown that features a map created with Leaflet. Host your webpage on either GitHub Pages, RPubs, or NeoCities. Your webpage must contain the date that you created the document, and it must contain a map created with Leaflet. We would love to see you show off your creativity!

My map is going to show my 4 top favorite football stadiums in mexico.

The data frame have 4 point with the geo-coordenates of my 4-top favorite stadiums in mexico. The places includes the states in order use them for color.

```{r}
library(leaflet)

lats<-c(21.880631, 20.681696,25.668442,19.303063)
longs<-c(-102.275539, -103.462849, -100.244473,-99.150549)
places<-c('Victoria Stadium', 'Akron Stadium', 'BBVA Stadium','Azteca Stadium')
states<-c('Aguascalientes', 'Jalisco', 'Nuevo Leon','CDMX')
df<-data.frame(lat=lats, lng=longs, places=places, states=states, statecolor=c("gray","red","blue","yellow") )
```

### Plotting the map using leaflet

```{r}
df%>%leaflet()%>%addTiles()%>%addCircleMarkers(color=df$statecolor, popup = df$places) %>% addLegend(labels = states[1:4], colors=c("gray","red","blue","yellow")) %>% addProviderTiles(providers$OpenStreetMap)
```